---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# steamr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

`steamr` is an R interface to the official
[Web API](https://steamcommunity.com/dev) of the Steam game store. The
package also provides access to Steam's
[undocumented storefront API](https://github.com/Revadike/InternalSteamWebAPI).
The package aims to provide a way to easily perform data collection based on
Steam data. It thus only implements API methods are can be used to retrieve
data sets for data analysis. 

## Installation

You can install the development version of steamr like so:

``` r
pak::install("jslth/steamr")
```

## Example

`steamr` implements most important data collection functions from both the
official Web API and the internal storefront API of Steam. Many functions operate
around a so-called application ID or `appid`. One way to find the app ID for a
game is to search for it programmatically:

```{r example}
library(steamr)
apps <- search_apps("team fortress")
appid <- apps$appid
apps
```

Many functions need an app ID to work, for example the following function which
retrieves user review data from an application:

```{r}
get_app_reviews(appid[1])
```

Steam can also use the official Web API given a valid API key. One function
offered by the Web API allows us to query details on a Steam application:

```{r}
get_items(appid)
```

