---
title: "Converting Steam IDs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Converting Steam IDs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(steamr)
```

The Steam API uses a variety of IDs. From user IDs, clan IDs and game
group IDs to more special cases like curator IDs or recommendation IDs,
identifying things in Steam works using strings of numerical mumbo-jumbo. 
This can become quite inconvenient if there are multiple types of the same
ID. This is the case for Steam IDs which can identify users, groups, and
game groups. Steam IDs can take four forms: 

- **Vanity IDs**: Human-readable account name given by the user
- **Steam64 IDs**: 64-bit representations of account information
- **Steam2 IDs**: Text representations of account information
- **Steam3 IDs**: Slightly more useful text representations of account information

It is important to be able to convert between these IDs. Usually, vanity IDs
are used wherever accounts are handled and shared by users. Steam64 is
machine-readable and often used in API methods. Steam2 and Steam3 contain the
most important information in relatively easy to access ways. Each ID type
(except vanity) consists of five components: Authentication server (or simply
Y), account number (or Z), instance, type, and universe (or X).

The authentication server can be 0 or 1. If the account number is even,
it is 0, otherwise it is 1. The account number is a unique number of a
user account. The instance is a number between 0 and 4 that tells us if the
account is a desktop instance (1), console instance (2), web distance (4), or
all at once (0). The account type identifies whether we are dealing with a
user or individual (1), group (7), or something else (e.g., a cypercafe
account or game server). Finally, the universe can be a number between 0 and 5
but is mostly set to 1 (public). 0 (unspecified), 2 (beta), and 3 (internal)
are also possible. 4 and 5 are legacy universes and do not really exist.

`steamr` supports conversions and parsing of Steam IDs. It is built on the
popular [SteamID php library](https://github.com/xPaw/SteamID.php/) and powered
by the [`gmp`](https://cran.r-project.org/web/packages/gmp/) and
[`bigBits`](https://cran.r-project.org/web/packages/bigBits/index.html)
packages for high-precision arithmetics and logical operations. More information
on Steam IDs can be found on the
[official wiki](https://developer.valvesoftware.com/wiki/SteamID).

## Conversions

To convert between different types of IDs, we can use the
`convert_steamid` function. To convert from or to vanity IDs, an API key is
required to be set.

```{r}
vanities <- c("BeFoRE-CS", "vgenkin")
steam64 <- convert_steamid(vanities, to = "steam64")
steam64
```

```{r}
steam2 <- convert_steamid(steam64, to = "steam2")
steam2
```

```{r}
steam3 <- convert_steamid(steam2, to = "steam3")
steam3
```

```{r}
convert_steamid(steam3, to = "vanity")
```

While conversions between Steam64, Steam2 and Steam3 can be done by applying
some high-precision logical operations, resolving vanity IDs requires
communicating with the Steam Web API. Vanity conversions are powered by
the `ResolveVanityURL` endpoint in the `resolve_vanity_url` function. Here,
we can also specify the type of profile, i.e. profile, group, or game group.
For example, we can look up the name of the
[official Valve group](https://steamcommunity.com/groups/Valve):

```{r}
resolve_vanity_url("Valve", type = "group")
```
```{r}
lookup_steamid("Valve", vanity_type = "group")
```



One way to get these converted IDs in a tidy dataframe is to use the
`lookup_steamid` function.

```{r}
lookup_steamid(vanities)
```

## Parsing

If we are interested in the internals of the Steam IDs, `steamr` provides
parsing functions for Steam64, Steam3, and Steam2 IDs. All parsing functions
return dataframes and work on vectors.

```{r}
steam64 <- c(steam64, "103582791429521412")
parse_steam64(steam64)
```

```{r}
parse_steam2(steam2)
```

```{r}
steam3 <- c(steam3, "[g:1:4]")
parse_steam3(steam3)
```



